Surface-driven registration method for the structure-informed segmentation of diffusion MR images\tnoteref{t1}

### 2015-11-03 Publications/2015-NeuroImage/02-abstract.tex
recover changes in abstract

% -*- root: 00-main.tex -*-
Current methods for processing \gls*{dmri} to map the connectivity of the human brain
  require precise delineations of anatomical structures.
\revcomment[C1 (R.1)]{%
The requirement has been approached either segmenting the data in native \gls*{dmri} space
  or projecting the structural information from \gls*{t1} images.
The characteristic features of diffusion data in terms of \acrlong*{snr}, resolution, etc.
  and the geometrical distortions caused by the inhomogeneity of magnetic susceptibility
  across tissues render the problem challenging.}
\revcomment[C10 (R.2)]{%
To solve the problem in a unified approach, we propose \regseg{}, a surface-to-volume nonlinear
  registration method that segments homogeneous regions within multivariate images by mapping
  a set of nested reference-surfaces.}
\revcomment[C11 (R.2)]{%
The surfaces can be extracted from the \gls*{t1} image of the subject, and the target image
  is the bivariate volume comprehending the \gls*{fa} and the \gls*{adc} maps derived from the
  \gls*{dmri} dataset.}
We first verify the subpixel accuracy of \regseg{} on digital phantoms, to then propose an
  evaluation framework that uses \gls*{dmri} datasets from the \gls*{hcp}.
In this framework, the undistorted \gls*{dmri} undergo a known distortion derived from real
  fieldmaps.
We analyze the misregistration error of the surfaces estimated by \regseg{} on 16 datasets.
The distribution of errors shows a 95\% CI of 0.56--0.66 mm, below the \gls*{dmri} resolution
  (1.25 mm, isotropic).
Finally, we cross-compare the proposed tool against a nonlinear \lowb{}-to-T2w registration
  method, thereby obtaining a significantly lower misregistration error with \regseg{}.

>>>>

% -*- root: 00-main.tex -*-
Current methods for processing \gls*{dmri} to map the connectivity of the human brain
  require precise delineations of anatomical structures.
\revcomment[C1 (R.1)]{%
This requirement has been approached either segmenting the data in native \gls*{dmri} space
  or mapping the structural information from \gls*{t1} images.
The characteristic features of diffusion data in terms of \acrlong*{snr}, resolution, as well
  as the geometrical distortions caused by the inhomogeneity of magnetic susceptibility
  across tissues hinder both solutions.}
\revcomment[C10 (R.2)]{%
Unifying the two approaches, we propose \regseg{}, a surface-to-volume nonlinear
  registration method that segments homogeneous regions within multivariate images by mapping
  a set of nested reference-surfaces.}
\revcomment[C11 (R.2)]{%
Accurate surfaces are extracted from a \gls*{t1} image of the subject, using as target image
  the bivariate volume comprehending the \gls*{fa} and the \gls*{adc} maps derived from the
  \gls*{dmri} dataset.}
\revcomment[rephrased]{%
We first verify the accuracy of \regseg{} on a general context using digital phantoms.
Then we establish an evaluation framework using undistorted \gls*{dmri} data from the \gls*{hcp}
  and known deformations derived from real inhomogeneity fieldmaps.
We analyze the performance of \regseg{} computing the misregistration error of the surfaces estimated
  after being mapped with \regseg{} onto 16 datasets from the \gls*{hcp}.
The distribution of errors shows a 95\% CI of 0.56--0.66 mm, that is below the \gls*{dmri}
  resolution (1.25 mm, isotropic).
Finally, we cross-compare the proposed tool against a nonlinear \lowb{}-to-T2w registration
  method, thereby obtaining a significantly lower misregistration error with \regseg{}.}
